Modelling the Lymphatic Metastatic Progression Pathways of OPSCC from Multi-Institutional Datasets

### 2023-12-15 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{table}
    \centering
    \variable{output/results_table.tex}
    \caption{Model comparison results from the base graph and the extended graph we chose as the ``winning'' model. For both \glspl{dag} we show the log-evidence, computed via thermodynamic integration, the negative one half of the \gls{bic}, as well as the maximum log-likelihood that was encountered during the final \gls{mcmc} sampling round.}
    \label{table:evidence}
\end{table}

>>>>

% \begin{table}
%     \centering
%     \variable{output/results_table.tex}
%     \caption{Model comparison results from the base graph and the extended graph we chose as the ``winning'' model. For both \glspl{dag} we show the log-evidence, computed via thermodynamic integration, the negative one half of the \gls{bic}, as well as the maximum log-likelihood that was encountered during the final \gls{mcmc} sampling round.}
%     \label{table:evidence}
% \end{table}

\begin{deluxetable}{lr}
    \tablecaption{Model comparison results from the base graph and the extended graph we chose as the ``winning'' model. For both \glspl{dag} we show the log-evidence, computed via thermodynamic integration, the negative one half of the \gls{bic}, as well as the maximum log-likelihood that was encountered during the final \gls{mcmc} sampling round. \label{table:evidence}}
    \tablehead{
        \textbf{graph}  & \textbf{log-evidence}
    }
    \startdata
    \variable{output/results_table.tex}
    \enddata
\end{deluxetable}
